l

### 2020-03-23 random/career_preparation/cover_letters/intel.tex
add bash yt-dl one-liner for wav

\documentclass[11pt,a4paper]{letter} % 10pt font size default, 11pt and 12pt are also possible
\renewcommand*\familydefault{\sfdefault}

\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
% \address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number

@@

\begin{letter}{Intel Corporation \\ 2200 Mission College Blvd \\ Santa Clara, CA  95052 }

@@

In senior year of high school, I was taking AP Computer Science Principles and we had to do two presentations. I did my first presentation on convolutional neural networks and my second on quantum computing. 
I didn’t realize until I learned more about complexity theory and big-O notation in college how amazing quantum systems are. 
This profound and numinous field of study is racing to Landauer's limit and has given me an exponentially greater appreciation for the beauty of nature.

I'm hoping to contribute some meaningful addition to helping us use NISQ devices to improve lives around the world.
As founder of the UChicago Quantum Society, I am hoping to bring back insights in how to communicate scientific works to general audiences and help grow the community of the quantum-curious.

\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}

>>>>

\documentclass[11pt]{letter} % 10pt font size default, 11pt and 12pt are also possible
\renewcommand*\familydefault{\sfdefault} 
\usepackage[margin=1in]{geometry}

\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
\address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number

@@

\begin{letter}{}

@@

Last spring, I started a club (ucquantum.org) for students interested in quantum information at UChicago, advised by Prof. Andrew Cleland.
I felt that there was a need for an academic club specifically for quantum technologies and NISQ computing.
This fall we began hosting weekly meetings and reaching out to various departments to find interested students.
Despite initially being slow going, our bimonthly newsletter covering news and Quantum research at UChicago has about 60 subscribers and we have a group of about 10 come each week.
The most rewarding part about this experience has been getting to explain superposition and entanglement to people.

Once we had learned the basics, we started planning events and reaching out to professors for when we got approved.
We toured Prof. David Schuster's superconducting qubit lab and spoke to a few professors about their work.
UChicago Quantum Society was approved to be an official club at the beginning of March.
I'm particularly excited about being able to host hackathons and panels with professors, unfortunately, students are off campus next quarter.

I believe that participating in quantum research and applications will give me insights into how to better teach and engage people with the field.
I'm hoping to use these experiences to be a more effective club president.

As a computer science major, I have been interested in the software used to control quantum devices.
I have used many of the quantum "languages" briefly (QISKit, Cirq, Quirk, etc), but after taking a course on Quantum Computation this quarter, I wanted to write my own quantum programming interface to learn how someone might make a fully featured simulator.

MyQuantum is a Julia-lang package that implements the common 1-bit operators (X, Y, Z, H), arbitrary controlled gate, and an arbitrary single-qubit rotation that can be composed with a control.
I also wrote functions to test if normalized, hermitian, unitary, added documentation, and unit tests.
I am looking to extend what I currently have to use as a pre-hackathon learners repo, to get people familiar with code and notation, but not be too advanced.

I am incredibly excited about the future of quantum computing and feel I have the necessary qualifications
to be a valuable team member in researching NISQ devices.

\begin{flushright}
    Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu
\end{flushright}

### 2020-03-23 random/career_preparation/cover_letters/qurip.tex
add bash yt-dl one-liner for wav

\documentclass[11pt,a4paper]{letter} % 10pt font size default, 11pt and 12pt are also possible
\renewcommand*\familydefault{\sfdefault}

@@

\begin{letter}{QURIP Internship}

@@

Almost every quantum scientist knows Feynmans’ holy quote, "Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical".

In senior year of high school, I was taking AP Computer Science Principles and we had to do two presentations. I did my first presentation on convolutional neural networks and my second on quantum computing. 
I didn’t realize until I learned more about complexity theory and big-O notation in college how amazing quantum systems are. 
This profound and numinous field of study is racing to Landauer's limit and has given me an exponentially greater appreciation for the beauty of nature.

I'm hoping to contribute some meaningful addition to helping us use NISQ devices to improve lives around the world.
As founder of the UChicago Quantum Society, I am hoping to bring back insights in how to communicate scientific works to general audiences and help grow the community of the quantum-curious.

\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}

>>>>

\documentclass[11pt]{letter} % 10pt font size default, 11pt and 12pt are also possible
\renewcommand*\familydefault{\sfdefault} 
\usepackage[margin=1in]{geometry}

@@

\begin{letter}{}

@@

Last spring, I started a club (ucquantum.org) for students interested in quantum information at UChicago, advised by Prof. Andrew Cleland.
I felt that there was a need for an academic club specifically for quantum technologies and NISQ computing.
This fall we began hosting weekly meetings and reaching out to various departments to find interested students.
Despite initially being slow going, our bimonthly newsletter covering news and Quantum research at UChicago has about 60 subscribers and we have a group of about 10 come each week.
The most rewarding part about this experience has been getting to explain superposition and entanglement to people.

Once we had learned the basics, we started planning events and reaching out to professors for when we got approved.
We toured Prof. David Schuster's superconducting qubit lab and spoke to a few professors about their work.
UChicago Quantum Society was approved to be an official club at the beginning of March.
I'm particularly excited about being able to host hackathons and panels with professors, unfortunately, students are off campus next quarter.

I believe that participating in QURIP will give me insights into how to better teach and engage people with the field.
I'm hoping to use these experiences to be a more effective club president.

As a computer science major, I have been interested in the software used to control quantum devices.
I have used many of the quantum "languages" briefly (QISKit, Cirq, Quirk, etc), but after taking a course on Quantum Computation this quarter, I wanted to write my own quantum programming interface to learn how someone might make a fully featured simulator.

MyQuantum is a Julia-lang package that implements the common 1-bit operators (X, Y, Z, H), arbitrary controlled gate, and an arbitrary single-qubit rotation that can be composed with a control.
I also wrote functions to test if normalized, hermitian, unitary, added documentation, and unit tests.
I am looking to extend what I currently have to use as a pre-hackathon learners repo, to get people familiar with code and notation, but not be too advanced.

I am incredibly excited about the future of quantum computing and feel I have the necessary qualifications
to be a valuable team member in researching NISQ devices.

\begin{flushright}
    Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu
\end{flushright}

### 2020-03-23 random/career_preparation/resume/resume2.tex
add bash yt-dl one-liner for wav

\section{COURSES}
\par
\normalfont{\textbullet{Abstract Linear Algebra}}
\normalfont{\textbullet{Algorithms}}
\normalfont{\textbullet{Computer Systems}}
\normalfont{\textbullet{Discrete Math}}\\
\normalfont{\textbullet{Electronics}}
\normalfont{\textbullet{Inventing Interactive Devices}}
\normalfont{\textbullet{Mathematical Logic}}\\
\normalfont{\textbullet{Molecular Engineering}}
\normalfont{\textbullet{Quantum Computation}}

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL\\
\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
\textbf{Spoken:} Fluent English. Classroom Hindi, Spanish, and Mandarin

@@

\textbf{codebyhand: applying handwriting recognition}\\ 
\textbullet{Wrote `paint` program that infers EMNIST characters after each stroke and allows transfer learning on own handwriting}\\
\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
\textbf{tools:} pytorch, torchvision, tkinter \\
\textbf{src :} github.com/anandijain/codebyhand\\

\section{ACTIVITIES}
\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
%-------------------------------------------------------------------------------
\end{resume}
\(\)\end{document}

>>>>

\section{COURSES}

\textbullet{Abstract Linear Algebra}
\textbullet{Algorithms}
\textbullet{Computer Systems}
\textbullet{Discrete Math}
\textbullet{Electronics}
\textbullet{Interactive Devices}
\textbullet{Mathematical Logic}
\textbullet{Molecular Engineering}
\textbullet{Quantum Computation}

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL, \LaTeX\\
\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
\textbf{Spoken:} Fluent English. Classroom Hindi, Spanish, and Mandarin

@@

\textbf{myquantum: the quantum learners repo}\\ 
\textbullet{Wrote basic quantum math package in Julia to learn/teach basic linear algebra}\\
\textbullet{Implements common 1-qubit gates, arbitrary 2-qubit control gates, arbitrary rotation}\\
\textbullet{Functions for checking if normed, unitary, hermitian, and generating Bell states}\\
\textbullet{Goal: Build circuit interface and perform QFT on my own simulated QC}\\
\textbf{tools:} Julia, LinearAlgebra.jl \\
\textbf{src :} github.com/anandijain/MyQuantum\\

\section{ACTIVITIES}
\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and QISKit}
%-------------------------------------------------------------------------------
\end{resume}
\(\)\end{document}
